Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-22 src/tex/ms.tex
Update content

% How to calculate the combined posterior
In figure \ref{fig:kappa_stacked}, we show the individual posterior of $\kappa$ of each events obtained from PE.
We assume $\kappa$ is different for each event, and the population distribution of $\kappa$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
We then performed hierarchical modeling to construct the likelihood function of $\mu$ and $\sigma$ given interferometer data.
To sample the posterior distribution of $\mu$ and $\sigma$, we used a generic sampling package, flowMC \citep{flowMC}, with prior of $\mu$ and $\sigma$ being uniform distributions.
The posterior of $\mu$ and $\sigma$ are shown in figure \ref{fig:corner_Gaussian}.

% Corner plot of mean and standard deviation of kappa
\begin{figure}[h]
    \script{corner_Gaussian.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian.pdf}
    \caption{
        The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
        2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        Orange line represent the median of $\mu$ and $\sigma$, which are \variable{output/mu_median.txt} and \variable{output/sigma_median.txt} respectively,.
        The mean of $\mu$ and $\sigma$ are \variable{output/mu_mean.txt} and \variable{output/sigma_mean.txt}, respectively.
    }
    \label{fig:corner_Gaussian}
\end{figure}

>>>>

% How to calculate the combined posterior
In figure \ref{fig:kappa_stacked}, we show the individual posterior of $\kappa$ of each events obtained from PE.
We assume $\kappa$ is different for each event, and the population distribution of $\kappa$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
We then performed hierarchical modeling to construct the likelihood function of $\mu$ and $\sigma$ given interferometer data.
To sample the posterior distribution of $\mu$ and $\sigma$, we used a generic sampling package, flowMC \citep{flowMC}, with prior of $\mu$ and $\sigma$ being uniform distributions.
The posterior of $\mu$ and $\sigma$ are shown in figure \ref{fig:corner_Gaussian}.
The mean of $\mu$ and $\sigma$ are \variable{output/Gaussian_mean.txt}, respectively.

% Corner plot of mean and standard deviation of kappa
\begin{figure}[h]
    \script{corner_Gaussian.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian.pdf}
    \caption{
        The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
        2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        Orange line represent the median of $\mu$ and $\sigma$.
    }
    \label{fig:corner_Gaussian}
\end{figure}
